Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-10-04 paper_comparison/paper_comparison/paper_comparison.Rmd
fix the first plot of analysis

What truly impress us is the huge difference between the estimated power of visual test and the estimated power of F-test. The margin is largest at around $log_e(E) = 2$. An example lineup is included in Figure \ref{fig:power-overview} where none of subjects detect the actual data plot positioned at panel 14. It demonstrates that at this level of difficulty, the designed visual feature is rarely visible, making the actual data plot indistinguishable from residual plots simulated from the assumed model. From a communication perspective, given the fact that the visual difference is unperceivable, the argument that non-linearity present in the fitted model is less convincing to the public even though it is true. At around $log_e(E) = 3$, the margin gets smaller as the chance of identifying the actual data plot becomes larger. At this level of difficulty, the designed visual features are usually detectable but it may not stand out from the lineup as other null plots may happen to include outliers or visual patterns that are are considered to be more attractive by human, and thus recognized as the most different plot. Without knowing the designed visual features beforehand, it is actually hard to identify the actual data plot by pure image comparison. The corresponding example lineup for $log_e(E) = 3$ shown in Figure \ref{fig:fig:power-poly-uniform} has the actual data plot positioned at panel 20, where two out of five subjects detect it. It can be observed that a M-shape is presented in plot 20, but the signal is not strong enough to attract all five subjects, resulting in a visual p-value sightly above the desired significance level $\alpha = 0.05$. At $log_e(E) = 4$ and $log_e(E) = 6$, the designed visual features become much clear and attractive, leading to a high percentage of rejection of the null hypothesis. Figure \ref{fig:fig:power-poly-uniform} gives example lineups of such cases. It is also interesting to observe that the power curve of visual test behaves similarly to those inappropriate conventional tests until the designed visual features really becomes visible.

@@

```{r fig:power-poly-uniform, fig.cap = "..."}
vi_survey_processed %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3) + 
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  theme_light(base_size = 5) -> p

VI_MODEL$plot_lineup(vi_lineup[["poly_39"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE)

VI_MODEL$plot_lineup(vi_lineup[["poly_415"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) -> p1

VI_MODEL$plot_lineup(vi_lineup[["poly_131"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) -> p2

VI_MODEL$plot_lineup(vi_lineup[["poly_322"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) -> p3

VI_MODEL$plot_lineup(vi_lineup[["poly_378"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) -> p4

@@

>>>>

What truly impress us is the huge difference between the estimated power of visual test and the estimated power of F-test. The margin is largest at around $log_e(E) = 2$. An example lineup is included in Figure \ref{fig:power-overview} where none of subjects detect the actual data plot positioned at panel 14. It demonstrates that at this level of difficulty, the designed visual feature is rarely visible, making the actual data plot indistinguishable from residual plots simulated from the assumed model. From a communication perspective, given the fact that the visual difference is unperceivable, the argument that non-linearity present in the fitted model is less convincing to the public even though it is true. At around $log_e(E) = 3$, the margin gets smaller as the chance of identifying the actual data plot becomes larger. At this level of difficulty, the designed visual features are usually detectable but it may not stand out from the lineup as other null plots may happen to include outliers or visual patterns that are are considered to be more attractive by human, and thus recognized as the most different plot. Without knowing the designed visual features beforehand, it is actually hard to identify the actual data plot by pure image comparison. The corresponding example lineup for $log_e(E) = 3$ shown in Figure \ref{fig:fig:power-poly-uniform} has the actual data plot positioned at panel 17, where two out of five subjects detect it. It can be observed that a "U-shape" is presented in plot 17, but the signal is not strong enough to attract all five subjects, resulting in a visual p-value sightly above the desired significance level $\alpha = 0.05$. At $log_e(E) = 4$ and $log_e(E) = 5$, the designed visual features become much clear and attractive, leading to a high percentage of rejection of the null hypothesis. Figure \ref{fig:fig:power-poly-uniform} gives example lineups of such cases. It is also interesting to observe that the power curve of visual test behaves similarly to those inappropriate conventional tests until the designed visual features really becomes visible.

@@

```{r fig:power-poly-uniform, fig.cap = "..."}
vi_survey_processed %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3) + geom_point(data = ~filter(.x, unique_lineup_id %in% c("poly_42", "poly_562", "poly_217", "poly_120")), aes(log_effect_size, prop_detect), alpha = 1, col = "red", size = 2) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  theme_light(base_size = 5) -> p

VI_MODEL$plot_lineup(vi_lineup[["poly_42"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 2~","~"F-test p-value" == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_42")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_42")$p_value_select_all_plots[1], digits = 3)))) -> p1

VI_MODEL$plot_lineup(vi_lineup[["poly_562"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 3~","~"F-test p-value" == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_562")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_562")$p_value_select_all_plots[1], digits = 3)))) -> p2

VI_MODEL$plot_lineup(vi_lineup[["poly_217"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 4~","~"F-test p-value" == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_217")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_217")$p_value_select_all_plots[1], digits = 3)))) -> p3

VI_MODEL$plot_lineup(vi_lineup[["poly_120"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 2~","~"F-test p-value" == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_120")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_120")$p_value_select_all_plots[1], digits = 3)))) -> p4

@@

```{r eval = FALSE}
vi_survey_processed %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
filter(abs(log(effect_size) - 3) < 0.2)

vi_survey_processed %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_abline() +
  geom_point(aes(p_value_uniform, p_value_select_all_plots)) +
  scale_x_log10() +
  scale_y_log10()
```

### 2022-10-04 paper_comparison/paper_comparison/paper_comparison.tex
fix the first plot of analysis

Diagnosing a model is the key to determining whether there is anything
importantly wrong. For linear regression analysis, it is typical to
interrogate the residuals. Residuals summarise what is not captured by
the model, and thus provide the capacity to identify what might be
wrong. There are many ways that residuals could be assessed.

Residuals might be plotted, as a histogram or quantile-quantile plot to
examine the distribution. Using the classical normal linear regression
model as an example, if the distribution is symmetric and unimodal, it
is well-behaved. But if the distribution is skewed, bimodal, multimodal,
or contains outliers, there is cause for concern. The distribution could
also be inspected by conducting a goodness of fit test, such as the
Shapiro-Wilk Normality test \citep{shapiro1965analysis}.

Plotting the residuals against predicted values and each of the
explanatory variables on a scatter plot is a recommend way to scrutinize
their relationships. If there is any visually discoverable patterns, the
model is potentially misspecified. However, it is a very difficult task
for a human judge, though to make a decision that there's nothing there.
It is especially common, particularly among new data analysts to report
patterns when an experienced data analyst might quickly conclude that
there are none. Generally, one looks for departures from nothingness
like non-linear dependency or heteroskedasticity. It is also possible to
conduct hypothesis tests for non-linear dependence
\citep{ramsey_tests_1969}, and use a Breusch-Pagan test
\citep{breusch_simple_1979} for heteroskedasticity.

There is an abundance of literature describing appropriate diagnostic
methods for linear regression: \citet{draper1998applied},
\citet{montgomery1982introduction}, \citet{belsley_regression_1980},
\citet{cook_applied_1999} and \citet{cook1982residuals}. The diligent
reader of these sage writings will also notice sentences that express
sentiments like \emph{based on their experience, statistical tests are
not widely used in regression diagnostics. The same or even larger
amount of information can be provided by diagnostic plots than the
corresponding tests in most empirical studies.} There is a common
guidance by experts that plots are the best for diagnosing model fits.

This is curious, and investigating why this might be common advice is
the subject of this paper. The paper is structured as follows. The next
background section describes the the types of departures that one
expects to detect, and describes a formal process for reading residual
plots, called visual inference, that can avoid the concerns about
subjectiveness of human readers. Section \ref{experimental-design}
describes the experimental setup to enable a comparison between decision
made by formal hypothesis testing, and how humans would read diagnostic
plots. The results are reported in Section \ref{results}. We finish with
a discussion on future work, in particular how the responsibility for
residual plot reading might be passed on to computer vision.

@@

Non-linearity, heterskedasticity and non-normality are perhaps the three
mostly commonly checked departures. Non-linearity is a type of model
misspecification caused by failing to include higher order terms of the
regressors in the regression equation. Any non-linear functional form of
residuals on fitted values presented in the residual plot could be
considered as an indicative of non-linearity. An example residual plot
containing visual pattern of non-linearity is given at the top-right of
Figure {[}ref here{]}. One can clearly observe the ``S-shape'' from the
residual plot as the cubic term is not captured by the misspecified
model. Heterskedasticity refers to the presence of nonconst error
variance in a regression model. It is mostly due to the strict but false
assumptions on the variance-covariance matrix of the error term. The
usual pattern of heterskedasticity on a residual plot is the
inconsistent spread of the residuals at different x values. Visually, it
sometimes results in the so-called ``butterfly'' shape as shown in the
bottom-left panel of Figure \ref{fig:residual-plot-common-departures},
or the ``left-triangle'' and ``right-triganle'' shape where the smallest
variance occurs at the edges of the x-axis. Compared to non-linearity
and heterskedasticity, non-normality is usually harder to be detected
from a residual plot since scatter plot is not excel in revealing
marginal distribution. A favourable graphical summarise for this task is
the quantile-quantile plot. However, for a consistent comparison in the
later part of this paper, residual plot will be the focus. Besides, it
is important to note that not all regression models assume normality for
the error term, but a certain amount do including the classical normal
linear regression model. In the case that the normality assumption is
violated, it is expected to observe data points that do not centralize
around the horizontal zero line and unevenly distribute at both sides of
the zero line. For example, given a skewed error distribution, fewer
data points and more outliers are on one side of the zero line as shown
at the bottom-right of Figure \ref{fig:residual-plot-common-departures}.

@@

Example residual plots given in Figure
\ref{fig:residual-plot-common-departures} are examined by the
corresponding model structural test, Breusch-Pagan test and
Shapiro--Wilk test as shown in Table
\ref{tab:example-residual-plot-table}. In the example, both the
Breusch-Pagan test and the Shapiro--Wilk test rejects the null
hypothesis for departures that they do not intend to examine. As
discussed in \citet{cook1982residuals}, most residual-based tests for a
particular type of departure from model assumptions are sensitive to
other types of departures. It is likely the null hypothesis is correctly
rejected but for the wrong reason, which is known as the ``Type III
error''. Additionally, outliers will often incorrectly trigger the
rejection of the null hypothesis despite the residuals are well-behaved
\citep{cook_applied_1999}. This can be largely avoided in diagnostic
plots as experienced analysts can evaluate the acceptability of
assumptions flexibly, even in the presence of outliers.

@@

What truly impress us is the huge difference between the estimated power
of visual test and the estimated power of F-test. The margin is largest
at around \(log_e(E) = 2\). An example lineup is included in Figure
\ref{fig:power-overview} where none of subjects detect the actual data
plot positioned at panel 14. It demonstrates that at this level of
difficulty, the designed visual feature is rarely visible, making the
actual data plot indistinguishable from residual plots simulated from
the assumed model. From a communication perspective, given the fact that
the visual difference is unperceivable, the argument that non-linearity
present in the fitted model is less convincing to the public even though
it is true. At around \(log_e(E) = 3\), the margin gets smaller as the
chance of identifying the actual data plot becomes larger. At this level
of difficulty, the designed visual features are usually detectable but
it may not stand out from the lineup as other null plots may happen to
include outliers or visual patterns that are are considered to be more
attractive by human, and thus recognized as the most different plot.
Without knowing the designed visual features beforehand, it is actually
hard to identify the actual data plot by pure image comparison. The
corresponding example lineup for \(log_e(E) = 3\) shown in Figure
\ref{fig:fig:power-poly-uniform} has the actual data plot positioned at
panel 20, where two out of five subjects detect it. It can be observed
that a M-shape is presented in plot 20, but the signal is not strong
enough to attract all five subjects, resulting in a visual p-value
sightly above the desired significance level \(\alpha = 0.05\). At
\(log_e(E) = 4\) and \(log_e(E) = 6\), the designed visual features
become much clear and attractive, leading to a high percentage of
rejection of the null hypothesis. Figure
\ref{fig:fig:power-poly-uniform} gives example lineups of such cases. It
is also interesting to observe that the power curve of visual test
behaves similarly to those inappropriate conventional tests until the
designed visual features really becomes visible.

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/fig:power-poly-uniform-1} \caption{...}\label{fig:fig:power-poly-uniform-1}
\end{figure}
\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/fig:power-poly-uniform-2} \caption{...}\label{fig:fig:power-poly-uniform-2}
\end{figure}

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-6-1}

>>>>

Diagnosing a model is the key to determining whether there is anything
importantly wrong. For linear regression analysis, we typically
interrogate the residuals for model diagnostics. Residuals summarise
what is not captured by the model, and thus provide the capacity to
identify what might be wrong.

We can assess residuals in multiple ways. Residuals might be plotted, as
a histogram or quantile-quantile plot to examine the distribution. Using
the classical normal linear regression model as an example, if the
distribution is symmetric and unimodal, it is well-behaved. But if the
distribution is skewed, bimodal, multimodal, or contains outliers, there
is cause for concern. The distribution could also be inspected by
conducting a goodness of fit test, such as the Shapiro-Wilk Normality
test \citep{shapiro1965analysis}.

Plotting the residuals against predicted values and each of the
explanatory variables on a scatter plot is a recommend way to scrutinize
their relationships. If there is any visually discoverable patterns, the
model is potentially misspecified. However, correctly judging a residual
plot where no pattern exists is a painstakingly difficult task for
humans. It is especially common, particularly among new data analysts to
report patterns when an experienced data analyst might quickly conclude
that there are none. {[}ET: I don't know if the former statement is
true?{]} Generally, one looks for noticeable departures from the model
like non-linear dependency or heteroskedasticity. It is also possible to
conduct hypothesis tests for non-linear dependence
\citep{ramsey_tests_1969}, and use a Breusch-Pagan test
\citep{breusch_simple_1979} for heteroskedasticity.

Abundance of literature describe appropriate diagnostic methods for
linear regression: \citet{draper1998applied},
\citet{montgomery1982introduction}, \citet{belsley_regression_1980},
\citet{cook_applied_1999} and \citet{cook1982residuals}. The diligent
reader of these sage writings will also notice sentences that express
sentiments like \emph{based on their experience, statistical tests are
not widely used in regression diagnostics. The same or even larger
amount of information can be provided by diagnostic plots than the
corresponding tests in most empirical studies.} A common guidance by
experts is that optimal method for diagnosing model fits is by plotting
the data.

The persistence of this advice to check the plots is curious, and
investigating why this might be common advice is the subject of this
paper. The paper is structured as follows. The next background section
describes the types of departures that one expects to detect, and
describes a formal process for reading residual plots, called visual
inference, that can avoid the concerns about subjectiveness of human
readers {[}ET: CITATION HERE?{]}. Section \ref{experimental-design}
describes the experimental setup to compare the decision made by formal
hypothesis testing, and how humans would read diagnostic plots. The
results are reported in Section \ref{results}. We finish with a
discussion on future work, in particular how the responsibility for
residual plot reading might be passed on to computer vision.

@@

Non-linearity, heterskedasticity and non-normality are perhaps the three
mostly checked departures. Non-linearity is a type of model
misspecification caused by failing to include higher order terms of the
regressors in the regression equation. Any non-linear functional form of
residuals on fitted values presented in the residual plot could be
considered as an indicative of non-linearity. An example residual plot
containing visual pattern of non-linearity is given at the top-right of
Figure \ref{fig:commondepartures}. One can clearly observe the
``S-shape'' from the residual plot as the cubic term is not captured by
the misspecified model.

Heteroskedasticity refers to the presence of nonconstant error variance
in a regression model. It is mostly due to the strict but false
assumptions on the variance-covariance matrix of the error term. The
usual pattern of heteroskedasticity on a residual plot is the
inconsistent spread of the residuals across the horizontal axis.
Visually, it sometimes results in the so-called ``butterfly'' shape as
shown in the bottom-left panel of Figure \ref{fig:commondepartures}, or
the ``left-triangle'' and ``right-triangle'' shape where the smallest
variance occurs at one side of the horizontal axis.

Compared to non-linearity and heteroskedasticity, non-normality is
usually harder to detect from a residual plot since scatter plot do not
readily reveal the marginal distribution. A favourable graphical summary
for this task is the quantile-quantile plot. However, for a consistent
comparison, residual plot will be the focus of this paper. Besides, it
is important to note that not all regression models assume normality for
the error term, but a certain amount do including the classical normal
linear regression model. In the case that the normality assumption is
violated, it is expected to observe data points do not center around the
horizontal axis and there is an uneven distribution of the number points
at both below and above the horizontal axis. For example, given a skewed
error distribution, fewer data points and more outliers are on one side
of the horizontal axis as shown at the bottom-right of Figure
\ref{fig:commondepartures}.

@@

Example residual plots given in Figure \ref{fig:commondepartures} are
examined by the corresponding model structural test, Breusch-Pagan test
and Shapiro--Wilk test as shown in Table
\ref{tab:example-residual-plot-table}. In the example, both the
Breusch-Pagan test and the Shapiro--Wilk test rejects the null
hypothesis for departures that they do not intend to examine. As
discussed in \citet{cook1982residuals}, most residual-based tests for a
particular type of departure from model assumptions are sensitive to
other types of departures. It is likely the null hypothesis is correctly
rejected but for the wrong reason, which is known as the ``Type III
error''. Additionally, outliers will often incorrectly trigger the
rejection of the null hypothesis despite when majority of the residuals
are well-behaved \citep{cook_applied_1999}. This can be largely avoided
in diagnostic plots as experienced analysts can evaluate the
acceptability of assumptions flexibly, even in the presence of outliers.

@@

What truly impress us is the huge difference between the estimated power
of visual test and the estimated power of F-test. The margin is largest
at around \(log_e(E) = 2\). An example lineup is included in Figure
\ref{fig:power-overview} where none of subjects detect the actual data
plot positioned at panel 14. It demonstrates that at this level of
difficulty, the designed visual feature is rarely visible, making the
actual data plot indistinguishable from residual plots simulated from
the assumed model. From a communication perspective, given the fact that
the visual difference is unperceivable, the argument that non-linearity
present in the fitted model is less convincing to the public even though
it is true. At around \(log_e(E) = 3\), the margin gets smaller as the
chance of identifying the actual data plot becomes larger. At this level
of difficulty, the designed visual features are usually detectable but
it may not stand out from the lineup as other null plots may happen to
include outliers or visual patterns that are are considered to be more
attractive by human, and thus recognized as the most different plot.
Without knowing the designed visual features beforehand, it is actually
hard to identify the actual data plot by pure image comparison. The
corresponding example lineup for \(log_e(E) = 3\) shown in Figure
\ref{fig:fig:power-poly-uniform} has the actual data plot positioned at
panel 17, where two out of five subjects detect it. It can be observed
that a ``U-shape'' is presented in plot 17, but the signal is not strong
enough to attract all five subjects, resulting in a visual p-value
sightly above the desired significance level \(\alpha = 0.05\). At
\(log_e(E) = 4\) and \(log_e(E) = 5\), the designed visual features
become much clear and attractive, leading to a high percentage of
rejection of the null hypothesis. Figure
\ref{fig:fig:power-poly-uniform} gives example lineups of such cases. It
is also interesting to observe that the power curve of visual test
behaves similarly to those inappropriate conventional tests until the
designed visual features really becomes visible.

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/fig:power-poly-uniform-1} \caption{...}\label{fig:fig:power-poly-uniform}
\end{figure}

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-7-1}
